Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex

A typical hybrid system, with a continuous plant and discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

@@

%------------------------------------
%\subsection{Using Fixed Point Arithmetic for verification}
%\label{fixedpoint_verification}
%------------------------------------

>>>>

\red{[where is this new variable used later?]}

A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$

@@

%------------------------------------
%\subsection{Using Fixed Point Arithmetic for verification}
%\label{fixedpoint_verification}
%------------------------------------
>>>>>>> 37d4cc3c530b25bf97f1052f7c187af06f832aea
